Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-22 manuscript/manuscript.Rmd
Use RCurl and R 3.2.0

```{r knitcitations_write, echo=FALSE, message=FALSE}
write.bibtex(file="knitcitations.bib")
# Also download Mendeley bibliography
download.file("https://www.dropbox.com/s/ehwm3c945k7rh0n/library.bib?dl=0", destfile="library.bib", method="curl", extra="-L")
```

>>>>

```{r knitcitations_write, echo=FALSE, message=FALSE}
write.bibtex(file="knitcitations.bib")
# Also download Mendeley bibliography
mendbib <- RCurl::getURL("https://www.dropbox.com/s/ehwm3c945k7rh0n/library.bib?dl=1", .opts=RCurl::curlOptions(followlocation=TRUE))
cat(mendbib, file="library.bib")
```
